Shannon diversity

### 2021-02-24 analysis/rev_prototyping/nsingletons.Rmd
get fia jks and restart fia not jk runs

all_di <- read.csv(here::here("analysis", "rev_prototyping", "all_di.csv"), stringsAsFactors = F)

@@

@@

<!-- ```{r} -->

<!-- ggplot(filter(all_di, nsingletons >= nsingletons_95), aes(nsingletons_mean, nsingletons)) + -->
<!--   geom_point(alpha = .2) + -->
<!-- #  geom_line(aes(nsingletons_mean, nsingletons_mean)) + -->
<!--     geom_line(aes(nsingletons_95, nsingletons_95)) + -->
<!--   facet_wrap(vars(dat), scales = "free") -->

<!-- ggplot(filter(all_di, nsingletons >= nsingletons_95), aes(nsingletons, nsingletons-nsingletons_95)) + -->
<!--   geom_point(alpha = .2) + -->
<!-- #  geom_line(aes(nsingletons_mean, nsingletons_mean)) + -->
<!--   facet_wrap(vars(dat), scales = "free") -->
<!-- ``` -->

>>>>

all_di <- read.csv(here::here("analysis", "reports", "all_di.csv"), stringsAsFactors = F)

@@

all_di <- all_di %>%
  mutate(singletons_change = (nsingletons - nsingletons_95) / s0)

ggplot(filter(all_di, high_singles_ex), aes(singletons_change)) +
  geom_histogram() +
  facet_wrap(vars(dat), scales = "free")

all_di %>%
  filter(high_singles_ex) %>%
  group_by(dat) %>%
  summarize(mean_singles_change = mean(singletons_change),
            n = dplyr::n())

@@
